---
title: "Validation of invasion"
output: github_document
author: "Almorò Scarpa"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
With this validation we wanted to prove that the simulator will generate on average
the number of insertions predicted by the equation:
$$c_{t}=c_{0}(1+\mu)^t$$
$c_{t}$ TE copies at generation t

$c_{0}$ TE copies at generation 0

$\mu$   Transposition rate

$t$     Generation


### Initial conditions:

$c_{0}=10$

$\mu = 0.1$

$t=100$

A chromosome of size 1Mb and no piRNA clusters.
We used 500 replicates

## Materials & Methods
version: invadego0.2.1
seed: 1659093816078434000

### Commands for the simulation:

```{bash, eval=FALSE}
folder="/Users/ascarpa/Downloads/invadego_simulations/Paramutagenic_chain_reaction/Validation"
tool="/Users/ascarpa/invade-invadego/invadego021"

$tool --N 1000 --gen 100 --genome mb:1 --cluster kb:0 --rr 4 --rep 500 --u 0.1 --basepop 10 --silent --steps 1> $folder/validation_1
```


### Visualization in R

Setting the environment
``` {r prssure, message = FALSE}
library(ggplot2)
library(RColorBrewer)
library(plyr)
library(gridExtra)
theme_set(theme_bw())

```

Visualization: comparing the simulations with the prediction
```{r pressure, warning=FALSE}
cn<-seq(0,99,1)
res<-10*1.1^cn
theo<-data.frame(x=1:100,y=res)
validation<-read.table("validation_1")
names(validation)<-c("rep", "gen", "popstat", "fmale", "spacer_1", "fwte", "avw", "avtes", "avpopfreq", "fixed","spacer_2","phase","fwpirna","spacer_3","fwcli","avcli","fixcli","spacer_4","fwpar_yespi","fwpar_nopi",
                     "avpar","fixpar","spacer_5","piori")

gl<-ggplot()+geom_line(data=validation,aes(x=gen,group=rep,y=avtes*1000),alpha=0.15,size=0.3)+scale_y_log10()+geom_line(data=theo,aes(x=x,y=y),size=2)+theme(legend.position="none")+ylab("TE copies in population")+xlab("Generation")
plot(gl)
```


## Conclusions
The simulation matched the expectations.
Invadego accurately reproduces the expected exponential increase of TE copy numbers in a population with no piRNA clusters.